A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-27 dl-paper.tex
Minor fix

\begin{abstract} 
We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal $\K_2$-functor.
This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also one of the ingredients needed for the proof of the orthogonal $\K_2$-analogue of Serre's problem. The final result holds for general commutative rings containing $\tfrac{1}{2}$, however some of the intermediate steps in its proof are obtained without this assumption.
\end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

>>>>

\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal Steinberg groups.
$\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
 positive solution of which currently is only known in the case of linear Steinberg groups. \end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.
